### 2023-11-08 manuscript/manuscript.Rmd
Improve the caption and row descriptions of table 2

compounds_percent_assigned <- standards_compound_outcomes %>% 
  dplyr::filter(
    outcome %in% c(
      "Matched to m/z features",
      "Assigned"
    )
  ) %>% 
  tidyr::gather(
    sample,n,
    -outcome
  ) %>% 
  tidyr::spread(
    outcome,n
  ) %>% 
  dplyr::group_by(sample) %>% 
  dplyr::summarise(
    percent = {Assigned / `Matched to m/z features` * 100} %>% 
      signif(digits = 3)
  ) %>% 
  dplyr::pull(percent) %>% 
  purrr::set_names(c(
    'spiked_urine',
    'standards'
  )) %>% 
  as.list()
```

@@

```{r compound-frequencies}
standards_compound_outcomes %>%
  dplyr::mutate(
    outcome = outcome %>%
      stringr::str_replace_all(
        'm/z',
        '\\\\textit{m/z}'
      ) %>% 
      stringr::str_replace_all(
        '&',
        '\\\\&'
      )
  ) %>%
  dplyr::relocate(
    spiked_urine,
    .after = dplyr::everything()
  ) %>%
  dplyr::rename(
    ` ` = outcome,
    `Standards mix` = standards,
    `Spiked urine` = spiked_urine
  ) %>%
  kableExtra::kable(
    format = 'latex',
    booktabs = TRUE,
    escape = FALSE,
    linesep = '',
    align = c(
      rep('l',1),
      rep('r',2)
    ),
    caption = 'Molecular formula assignment results frequencies for the 64 unique molecular formulas of the chemical standards in the standards mix and spiked into human urine.'
  ) %>%
  kableExtra::kable_styling(
    latex_options = "HOLD_position"
  )
```

>>>>

compounds_percent_assigned <- standards_compound_outcomes %>% 
  dplyr::filter(
    outcome %in% c(
      "MFs matched to m/z features",
      "Total MFs assigned"
    )
  ) %>% 
  tidyr::gather(
    sample,n,
    -outcome
  ) %>% 
  tidyr::spread(
    outcome,n
  ) %>% 
  dplyr::group_by(sample) %>% 
  dplyr::summarise(
    percent = {`Total MFs assigned` / `MFs matched to m/z features` * 100} %>% 
      signif(digits = 3)
  ) %>% 
  dplyr::pull(percent) %>% 
  purrr::set_names(c(
    'spiked_urine',
    'standards'
  )) %>% 
  as.list()
```

@@

```{r compound-frequencies}
standards_compound_outcomes %>%
  dplyr::mutate(
    outcome = outcome %>%
      stringr::str_replace_all(
        'm/z',
        '\\\\textit{m/z}'
      ) %>% 
      stringr::str_replace_all(
        '&',
        '\\\\&'
      )
  ) %>%
  dplyr::relocate(
    spiked_urine,
    .after = dplyr::everything()
  ) %>%
  dplyr::rename(
    ` ` = outcome,
    `Standards mix` = standards,
    `Spiked urine` = spiked_urine
  ) %>%
  kableExtra::kable(
    format = 'latex',
    booktabs = TRUE,
    escape = FALSE,
    linesep = '',
    align = c(
      rep('l',1),
      rep('r',2)
    ),
    caption = 'Molecular formula assignment results for the 64 unique molecular formulas (MFs) of the chemical standards in the standards mix and spiked into human urine. The MFs assigned are also shown for the individual adduct and isotopic (A\\&I) iterations and the transformation (T) iterations.'
  ) %>%
  kableExtra::kable_styling(
    latex_options = "HOLD_position"
  )
```
